Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
modifications pictures

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{quivers}}
	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
	\label{fig:quivers}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.4]{koszulQuivers}}
	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
	\label{fig:koszulQuivers}
\end{figure}

@@

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the first four quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded (the second surface has no boundary, it is just a sphere).}
	\label{fig:examplesSurfaces}
\end{figure}
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded. The first surface is a cylinder, the second one is a torus with a hole.}
	\label{fig:examplesSurfaces2}
\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{example}[Double cycle]
\label{exm:doubleCycle}
Consider the following family of locally gentle quivers:
\vincent{TODO double cycle}
\end{example}

\begin{example}[Double path]
\label{exm:doublePath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}

>>>>

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{quivers}}
	\caption{Some locally gentle quivers and their blossoming quivers. Initial vertices are solid and labeled while blossom vertices are hollow, and initial arcs are bold while blossom arcs are thin.}
	\label{fig:quivers}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{koszulQuivers}}
	\caption{The Koszul duals of the (blossoming) quivers of \fref{fig:quivers}.}
	\label{fig:koszulQuivers}
\end{figure}

@@

This construction is illustrated on \fref{fig:examplesSurfaces}.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{examplesSurfaces}}
	\caption{The surface~$\surface_{\bar Q}$ for the quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded, and the glue symbols indicate how to identify some edges to get the desired surfaces. The first two surfaces are disks, the third is a sphere, the fourth is a cylinder, and the fifth is a punctured torus.}
	\label{fig:examplesSurfaces}
\end{figure}

%\begin{figure}[t]
%	\capstart
%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded. The first surface is a cylinder, the second one is a torus with a hole.}
%	\label{fig:examplesSurfaces2}
%\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

@@

\begin{example}[Cambrian paths]
\label{exm:CambrianPath}
\end{example}

\begin{example}[Double cycles]
\label{exm:doubleCycle}
Consider the following family of locally gentle quivers:
\vincent{TODO double cycle}
\end{example}

\begin{example}[Double paths]
\label{exm:doublePath}
Consider the following family of locally gentle quivers:
\vincent{TODO double path}
\end{example}
